Meta-analysis of the Interoceptive Accuracy Scale

### 2024-06-04 analysis/study1_a.qmd
Study1_a
The version that renders on my laptop.

---
title: "Meta-analysis of the Interoceptive Accuracy Scale"
subtitle: "Study 1"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: true
    toc: true
    fig-dpi: 100
    fig-width: 11.33
execute: 
  cache: true
---

```{r}
#| message: false
#| warning: false

@@

```{r}
load("../data/Gaggero2021/data.rda")
df2 <- data |> 
  mutate(Gender = as.character(gender)) |> 
  rename(
    Age=age, Heart = `IAS 1`, Hungry = `IAS 2`, Breathing = `IAS 3`, Thirsty = `IAS 4`,
    Urinate = `IAS 5`, Defecate = `IAS 6`, Taste = `IAS 7`, Vomit = `IAS 8`, Sneeze = `IAS 9`,
    Cough = `IAS 10`, Temp = `IAS 11`, Sex_arousal = `IAS 12`, Wind = `IAS 13`, Burp = `IAS 14`,
    Muscles = `IAS 15`, Bruise = `IAS 16`, Pain = `IAS 17`, Blood_Sugar = `IAS 18`,
    Affective_touch = `IAS 19`, Tickle = `IAS 20`, Itch = `IAS 21`)
rm(data)
```

@@

<!-- ##### Sample 10 -->

<!-- Bowling (2024) - https://osf.io/tx8h9/ -->

<!-- ```{r} -->
<!-- df10 <- haven::read_sav("../data/Bowling2024/TouchAttitudesData.sav") |> -->
<!--   mutate_all(as.numeric) |> -->
<!--   mutate(Gender = as.character(ifelse(Gender_coded == 1, "Male", ifelse(Gender_coded == 2, "Female", "Other")))) |> -->
<!--   rename( -->
<!--     Heart = IAS1, Hungry = IAS2, Breathing = IAS3, Thirsty = IAS4, -->
<!--     Urinate = IAS5, Defecate = IAS6, Taste = IAS7, Vomit = IAS8, Sneeze = IAS9, -->
<!--     Cough = IAS10, Temp = IAS11, Sex_arousal = IAS12, Wind = IAS13, Burp = IAS14, -->
<!--     Muscles = IAS15, Bruise = IAS16, Pain = IAS17, Blood_Sugar = IAS18, -->
<!--     Affective_touch = IAS19, Tickle = IAS20, Itch = IAS21 -->
<!--   )  -->

<!-- ``` -->

@@

## Graph Analysis

>>>>

---
title: "Meta-analysis of the Interoceptive Accuracy Scale"
subtitle: "Study 1"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: true
    toc: true
    fig-dpi: 100
    fig-width: 11.33
execute: 
  cache: true
---
```{r}
#| message: false
#| warning: false

@@

```{r}
load("../data/Gaggero2021/data.rda")
df2 <- data |> 
  mutate(Gender = as.character(gender)) |> 
  mutate(across(starts_with("IAS "), as.numeric)) |>
  rename(
    Age=age, Heart = `IAS 1`, Hungry = `IAS 2`, Breathing = `IAS 3`, Thirsty = `IAS 4`,
    Urinate = `IAS 5`, Defecate = `IAS 6`, Taste = `IAS 7`, Vomit = `IAS 8`, Sneeze = `IAS 9`,
    Cough = `IAS 10`, Temp = `IAS 11`, Sex_arousal = `IAS 12`, Wind = `IAS 13`, Burp = `IAS 14`,
    Muscles = `IAS 15`, Bruise = `IAS 16`, Pain = `IAS 17`, Blood_Sugar = `IAS 18`,
    Affective_touch = `IAS 19`, Tickle = `IAS 20`, Itch = `IAS 21`)
rm(data)
```

@@

@@

:::
## Graph Analysis
